---
title: "Tanaka_ReadingCleaningGenie"
output: html_document
date: "2026-01-28"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#Cleaning Genie Instructions

1. Make the words lowercase!
2. Do you want to get rid of anything? Numbers or ordinal numbers (Yes)
3. Split white space 
4. Remove punctuation; consider contractions before you remove the words, because they need to be expanded first
5. You can do if or if/else statements for the function
6. Include splitstring function 
7. Creative reign in my cleaning genie
```{r}

#We are loading the text into R! Here we have the unabomber text which needs to be thoroughly cleaned
badtoken <- paste(readLines('https://raw.githubusercontent.com/Reilly-ConceptsCognitionLab/reillylab_publicdata/main/unabomber_manifesto.txt'))

#I am providing the option to view certain texts from the unabomber texts; badtoken.s means we have shortened the the bad token text to view only a set amount of texts 
badtoken.s <- cat(badtoken[1:60], sep = "\n")

#Now, we start building the genie from the bottle! I will be annotating the the function heavily to become one with the function!

#The function will only take the input of the uncleaned (bad) token. The default is to view the token from 1-60, but the code for it can be blocked off so that all the text can be used
springcleaning <- function(badtoken.s) { 

# We are making all the stuff lower case! Have to start somewhere
  x <- tolower(badtoken.s)

#Next, we need to input replacement words; replace the slang!
  
  

#
  
# (N) Here we are removing punctuation from the token
  gonestring <- gsub("[[:punct:]]","",badtoken) 

#We are almost at the finish line, here we are splitting the string by spaces to create words
  splitstring = str_split(gonestring, " ")

#NOTE TO SELF: DO NOT INCLUDE this code since it will create a data frame that will crash your already slow laptop
  #df_lambchops <- data.frame(x = splitstring)
  #colnames(df_lambchops)[1] <- "Words"
  
  return(df_lambchops) 

} 


springcleaning(badtoken.s)



```

