---
title: "NLP Code Snippet Cheat Sheet"
author: "Tanaka"
date: "`r format(Sys.Date(), '%B %Y')`"
output:
  html_document:
    code_folding: show
    toc: true
    toc_float: true
    toc_depth: 2
    css: !expr here::here("/Users/tanakamanhede/Library/CloudStorage/OneDrive-TempleUniversity/Manhede_RData/styles_templates/jr_19.css")
---

```{r setup, include=F}
knitr::opts_chunk$set(fig.width=8, fig.height=5, fig.align = 'left', fig.path='Figs/', cache.path='Cache/', eval=T, echo=T, tidy=TRUE,  cache=F, message=F, warning=F, stringsAsFactors=F, yaml.eval.expr = TRUE)  

library(xfun)
pkg_attach("tidyverse", "here", "kableExtra", "RCurl", "psych", "knitr", "RColorBrewer", 'dplyr', 'gutenbergr', 'janeaustenr', install=T)

jamie.theme <- theme_bw() + theme(axis.line = element_line(colour = "black"), panel.grid.minor = element_blank(), panel.grid.major = element_blank(), panel.border = element_blank(), panel.background = element_blank(), legend.title= element_blank())  #custom theme ggplot2


print.me <- function(x, ...) {
if (nrow(x) > 200){
   len <- 200 
    } else {
       len <- (nrow(x))
}
   x[1:len,] %>%
   kbl(digits=2, align= 'l', booktabs=T) %>%
   kable_styling(fixed_thead = T) %>%
   kable_paper("striped", full_width = T, html_font = "Helvetica", font_size = 12) %>%
   row_spec(0, color = "white", background = "#5b705f", font_size = 12) %>%
   scroll_box(width = "700px", height = "500px") %>%
   asis_output()
}

registerS3method("knit_print", "data.frame", print.me)
#to_R <- read.csv(here("data", "MyRaw.txt")) ---- using 'here' to read in data
```

# Cheatsheet Code Snippets

Below are code snippets that will be continuously updated!


## Importing files from online repositories!
Are you tired of continuously updating file pathways to match your local file repository? Look no further
```{r}
#Here, I am loading in unabomber texts from an online repository!
test1 <- paste(readLines('https://raw.githubusercontent.com/Reilly-ConceptsCognitionLab/reillylab_publicdata/main/unabomber_manifesto.txt'))

```


## Make a function
You can make a function to build unique functions
```{r}
#Here, you can make your own function! The input of the function is a vector which the coder will insert any variable and will get the result due to the function containing select commands
myfunc <- function(x,y) { 

Z <- x+y 

return(Z) 

} 

#You can test myfunc here by simply inputting variables requested by the function

myfunc(3,2)

```


## Gsub (global substitution)
gsub is a great function that can remove and replace things you want and don't need  
```{r}
#Just loading in the some text
badtoken <- "Mary had a little lamb"
# The [[:punct:]] observes all punctuation in the token, the " " is to replaces the punctuation, and the "badtoken" is the variable or in other words the content or text you are looking to start cleaning
gonestring <- gsub("[[:punct:]]","",badtoken) 

```


## lowercase
if you want lowercase text, use this function!
```{r}
#Loading in a file to mess
badtoken <- "Mary Had A Little Lamb"

#Just a simple code to make the text lowercase!
x <- tolower(badtoken)

print(x)
```


## Splitting strings
Another easy code snippet worth mentioning since we are in the realm of NLP. This code is good when you want to tokenize the text you have.
```{r}
#Here is a few lines of code that we can to
gonestring <- "Mary had a little lamb"

splitstring = str_split(gonestring, " ")

```

# More code snippets to come...
