---
title: "Natural Language Processing Course"
author: "Tanaka Manhede"
date: "`r format(Sys.Date(), '%B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    css: !expr here::here("~/Documents/GitHub/project_nlpcourse26/Manhede_RData/styles_templates/tm_professional.css")
---

```{r setup, include=F}
knitr::opts_chunk$set(fig.width=8, fig.height=5, fig.align = 'left', fig.path='Figs/', cache.path='Cache/', eval=T, echo=T, tidy=TRUE,  cache=F, message=F, warning=F, stringsAsFactors=F, yaml.eval.expr = TRUE)  

library(xfun)
pkg_attach("tidyverse", "here", "kableExtra", "RCurl", "psych", "knitr", "RColorBrewer", 'dplyr', 'readr', install=T)

jamie.theme <- theme_bw() + theme(axis.line = element_line(colour = "black"), panel.grid.minor = element_blank(), panel.grid.major = element_blank(), panel.border = element_blank(), panel.background = element_blank(), legend.title= element_blank())  #custom theme ggplot2


print.me <- function(x, ...) {
if (nrow(x) > 200){
   len <- 200 
    } else {
       len <- (nrow(x))
}
   x[1:len,] %>%
   kbl(digits=2, align= 'l', booktabs=T) %>%
   kable_styling(fixed_thead = T) %>%
   kable_paper("striped", full_width = T, html_font = "Helvetica", font_size = 12) %>%
   row_spec(0, color = "white", background = "#5b705f", font_size = 12) %>%
   scroll_box(width = "700px", height = "500px") %>%
   asis_output()
}

registerS3method("knit_print", "data.frame", print.me)
#to_R <- read.csv(here("data", "MyRaw.txt")) ---- using 'here' to read in data


# dat <-
# need two columns assigning each word with the Nlett
#
#
#
#install.packages("formatR")
library(formatR)
```

# Introduction

This document serves as a central repository for assignments, and cleaning genies. The assignment section contains subsections highlighting a different coding assignment.

<br>

# Assignments

This segment contains all assignments

<br>

## Assignment 1

For the first assignment, I am going to produce a string called "Mary had a little lamb" in one code block. Then I am going to split the string to one word per row. Next, I am going to add a variable called Nletters that counts the letters in each word. The other part of the assignment is to style the css to personal needs.
<br>
So, step one is to produce the string "Mary had a Little Lamb"

```{r}
my_string <- "Mary had a little lamb"

print(my_string)

```

Now, we are going to take the string "Mary had a little lamb" and put it into a data frame that counts the number of letters/characters in each word. The challenge is being able to create a table that I can simply change the string and it will automatically update:

```{r}

#This splits the sentence by word, given that there is a space inserted between each word
words = str_split(my_string, " ")

#This is a data frame that serves to list out the words in the sentence and the number of letters or characters in each word. It has been formated this way so that a different sentence can be inserted and formatted as a data frame
df.lambchops <- data.frame(x = words, y = NA)

#I am renaming the column with more appropriate names. (haha lamb chops)
colnames(df.lambchops)[1] <- "Words"
colnames(df.lambchops)[2] <- "N_letters"

#For the N_letters column, here we are counting the number of characters or letters in each word that has its own row
df.lambchops$N_letters <- nchar(df.lambchops$Words)

print(df.lambchops)

```

<br>

## Assignment 2

Well it looks like we have another assignment, this one took a little more elbow grease than the last time...

First step is loading in the file needed to be cleaned.

1) Read 'sticks_messy.txt' into R

```{r}
#Here, I am loading in the messy_txt to clean
messy_txt <- readLines('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week2_nlp/data/sticks_messy.txt')
  
```
<br>

I combined the next steps into a function called springcleaning

2) Create a cleaning function with at least three chained procedures
3) Clean the text file using your homemade cleaning function
4) Split the text file into a one-word-per row format

```{r}

springcleaning <- function() { 

#This line removes punctuations and replaces it with no space to push the word token together or removes an extra space
  gonestring.punct <- gsub("[[:punct:]]","",messy_txt) 
#Removes numbers and replaces it with no space to push the word token togetheror removes an extra space
  gonestring.num <- gsub("[[:digit:]]","",gonestring.punct)
#Removes extra abnormal spaces and replaces it with one space to separate word tokens
  gonestring.sp <- gsub("[[:space:]]"," ", gonestring.num) 
#Splits the words by space
  splitstring = strsplit(gonestring.num, " ")
#Unlisting the texts in the file
  splitstring.unlist <- unlist(splitstring)
#This makes a data frame with a word per row
  df_lambchops <- data.frame(x = splitstring.unlist)
#A new data fram is made and excludes cells that are empty
  df_lamb <- df_lambchops %>% filter(x != "")

#Renaming the column for organizational purposes to "Words" instead of "x"
  colnames(df_lamb)[1] <- "Words"
#Returning a new data frame!
  return(df_lamb) 

} 

springcleaning()

```
<br>


5) Tell me how many words are in the story

```{r}
#I am counting the number of rows since it represents the number of words in the text
nrow(springcleaning())

```
<br>


6) Compute type token ratio

```{r}

ttr <- function() {
#Counting how many words are in the function to find the total word token
  tokens <- nrow(springcleaning())
#Counting the number of unique word tokens in the data frame
  type <- length(unique(springcleaning()$Words))
#Need to make the values of each variable numeric so that I can perform the operation;It will not work on characters
  as.numeric(tokens)
  as.numeric(type)
#Creating a formula to take the number of unique word tokens and divide it by the total number of tokens in the text
  TTR <- type/tokens
  
  return(TTR)
}

ttr()

```

All done! 

Keep an eye out for assignment 3!
<br>
<br>

## Assignment 3
<br>


```{r}

messy_txt <- readLines(
  "/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week2_nlp/data/sticks_messy.txt"
)

```



```{r}

springcleaning2.0 <- function() { 
  
#Loading in stop words from SMART and MIT 
load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/SMART_stops.rda')

load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/MIT_stops.rda')
  
load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/replacements_25.rda')

  
    messy_txt <- gsub("[[:digit:]]","",messy_txt)
    
  #Making all the words in the text lowercase
    gtext.low <- tolower(messy_txt)
    
  #Removing words from the SMART list
    gtext.smart <- gsub(paste0("\\b(", paste(SMART_stops$word, collapse="|"), ")\\b"), "", gtext.low)
  
  #Replacing contractions with their government names; I unlocked a new R code setNames
    gtext.cont <- str_replace_all(gtext.smart, setNames(replacements_25$replacement, replacements_25$word))
    
  #Removing stop words using MIT  (Most Important Text) 
    gtext.MIT <- gsub(paste0("\\b(", paste(MIT_stops$word, collapse="|"), ")\\b"), "", gtext.cont)
 
  #Removing erroneous punctuation from the text
    gtext <- gsub("[[:punct:]]","",gtext.MIT) 
    
  #Removing random spaces from the text
    gtext2 <- gsub("[[:space:]]"," ", gtext) 
              
  #Splits the words by space
    splitstring2.0 = strsplit(gtext2, " ")
    
  #Unlisting the texts in the file
    splitstring.unlist2.0 <- unlist(splitstring2.0)
    
  #This makes a data frame with a word per row (I like lamb chops (literally), so I kept it)
    df_lambchops2.0 <- data.frame(x = splitstring.unlist2.0)
    
  #A new data fram is made and excludes cells that are empty
    df_lamb2.0 <- df_lambchops2.0 %>% filter(x != "")
  
  #Renaming the column for organizational purposes to "Words" instead of "x"
    colnames(df_lamb2.0)[1] <- "Words"
    
  #Returning a new data frame!
    return(df_lamb2.0) 
} 


# *Cracks knuckles* Moment of truth
springcleaning2.0()

```

The function is now tested:

```{r}

#For my next feat, I have pulled texts from The Onion to test the cleaning genie2.0!
messy_txt <- c(
  "Facing intense backlash and scrutiny from critics who say the reference book publisher had failed to take all words into consideration, Merriam-Webster was accused of bias Monday after officially selecting ‘dictionary’ as its 2025 word of the year. “Merriam-Webster clearly has a pro-dictionary bias that’s preventing it from considering all words equally,” lexicographer Alison Nielsen wrote in a widely shared social media post that lambasted the Merriam-Webster editorial team, claiming its members had allowed a “personal affinity for looking up words” to cloud their judgment. “I was willing to overlook it last year when their word of the year was ‘definition,’ but I can’t allow myself to turn a blind eye to this. The Merriam-Webster editorial board is stuck in its own media bubble. They need to look around and read a thesaurus once in a while.” At press time, reports confirmed Merriam-Webster appeared to have doubled down by changing the 2025 word of the year to “dictionaries.”", 
  "“I love having this killer coat in the winter, especially when me and my buddies are cruising around and blasting tunes in my old Mustang, which doesn’t have any heat,” said Lockhart, stretching his lean frame over a pool table to sink a bank shot as he spoke to reporters about how he spends much of his time fixing up the muscle car, which has a faded King Cobra decal on the hood. “Bundle Up Our Bad Boys understands that when a guy like me looks good, he feels good. I’ve become more successful in all areas of my life, whether it’s picking up broads, fighting some jock who dissed me, or street racing at night around a deadly bend on the edge of town.”",
  "Stifling their groans as an instructor distributed the wailing infants, students at the Culinary Institute of America were reportedly given a live baby Friday to learn how to care for a bag of flour. “Flour is the most delicate of the pantry staples, and looking after this child for the week will prepare you to deal with the complexities of milled grain,” said Inès Allard, who teaches introduction to baking and pastry at the school, explaining that the students would have to keep the baby from leaking just as they would need to do with an actual sack of processed wheat. “I know it’s not a real bag of flour, but it’s important to take this seriously. And trust me, this is easy mode—babies can be left out in the open, but if you do that with flour, you get ants. If you can’t handle a live infant, then you sure as hell aren’t ready for 10 pounds of ultra-fine pizza flour crafted from the highest-quality varieties of soft wheat.” At press time, reports indicated that many students had already decided it would be too much work to have a flour bag of their own.")
```
All texts are courtesy of The Onion and their talented writers. Please view here: <a href="https://theonion.com/merriam-webster-accused-of-bias-after-dictionary-named-word-of-the-year/" target="_blank">The Onion: Dictionary</a>, <a href="https://theonion.com/community-leather-coat-drive-helps-bad-boys-in-need/" target="_blank">The Onion: Leather Jacket</a>, <a href="https://theonion.com/culinary-students-given-live-baby-to-learn-how-to-care-for-bag-of-flour/">The Onion: Chef Baby</a>

<br>
<br>


```{r}
springcleaning2.0()
```

## Assignment 4
1) Use Quanteda and base R for this assignment
2)Submit as HTML (link or file) using your own css styled output
3) Style it like a real report describing what you are doing at each step and why
4) Read in unabomber from my github repo
5) Output its structure

The unabomber text is analyzed. Here, the text is named "messy_txt"
```{r}
#Unabomber text is read in
messy_txt <- paste(readLines('https://raw.githubusercontent.com/Reilly-ConceptsCognitionLab/reillylab_publicdata/main/unabomber_manifesto.txt'))

```


A new cleaning genie for quanteda is made to output a text rather than a data frame
```{r}

raw_txt <- readLines(
  "https://raw.githubusercontent.com/Reilly-ConceptsCognitionLab/reillylab_publicdata/main/unabomber_manifesto.txt"
)

unabomb_quanteda <- function() { 
  
  #Loading in r data stopwords for cleaning
  load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/SMART_stops.rda')
  load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/MIT_stops.rda')
  load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/replacements_25.rda')
  
  # Standardizes font punctuation not recognized by code to be used in the function
  utf8_normalize <- function(x) {
    stringi::stri_enc_toutf8(as.character(x), is_unknown_8bit = FALSE, validate = TRUE)
  }
  
  # Replacing apostrophes and quotes
  unabomb_quanteda_unr.apos <- stringr::str_replace_all(
    utf8_normalize(x = raw_txt), 
    "[\u201c\u201d\u0022\u2033\u02dd\u201f\u201e]", " "
  )

  #Applies lowercase to all the text
  unabomb_quanteda_lower <- tolower(unabomb_quanteda_unr.apos)
  
  #Removing digits and spaces
  unabomb_quanteda_digits <- gsub("[[:digit:]]", " ", unabomb_quanteda_lower)
  unabomb_quanteda_space <- gsub("[[:space:]]", " ", unabomb_quanteda_digits)

  #Replacing contractions with the appropriate expansion  
  unabomb_quanteda_contractions <- stringr::str_replace_all(unabomb_quanteda_space, 
    setNames(replacements_25$replacement, nm = replacements_25$word))
 
  #Converting the stopwords columns from each data frame into appropriate form to be able to remove stop words
  sw <- unique(c(MIT_stops$word, SMART_stops$word))
  sw <- sw[nzchar(sw)]
  sw <- gsub("([][{}()+*^$|\\\\?.])", "\\\\\\1", sw)

  unabomb_quanteda_nostops <- gsub(
    paste0("\\b(", paste(sw, collapse = "|"), ")\\b"),
    "",
    unabomb_quanteda_contractions,
    perl = TRUE
  )

  # Removes punctuation except periods by replacing punctuation with spaces
  unabomb_quanteda_punct <- gsub("(?!\\.)[[:punct:]]", " ", unabomb_quanteda_nostops, perl = TRUE)
  #Replaces any and all whitespace into a single space
  unabomb_quanteda_final <- gsub("[[:space:]]+", " ", unabomb_quanteda_punct)
  
  #Cleans up any remaining spaces as a result of removal of punctuation
  unabomb_quanteda_final <- gsub("^ | $", "", unabomb_quanteda_final)

  return(unabomb_quanteda_final) 
}

```


The cleaned text is transformed into a corpus and a summary is generated.
```{r}
#Loading in the quanteda  library
library(quanteda)

#Assigning the unabomb_quanteda function into an object
clean_txt <- unabomb_quanteda()

#The data is converted to a corpus for further analysis 
my_simple_corpus <- corpus(clean_txt)

#The corpus is tokenized, removing numbers, punctuation, and separating space
clean_tokenized <- tokens(
  my_simple_corpus,
  remove_numbers = TRUE,
  remove_punct = TRUE,
  remove_separators = TRUE
)

#Showing data for the corpus 
summary(my_simple_corpus)

```


A table of lexical characteristics is generated
```{r}
#Creating a tokenized version of the corpus tokens_unabomb, removing punctuation and stopwords
tokens_unabomb <- tokens(clean_txt, remove_punct = TRUE) %>% tokens_remove(stopwords("SMART"))

#Creating a document-feature matrix, stemming is applied
md_dfm_unabomb <- dfm(tokens_unabomb, dfm_stem = TRUE)
topfeatures(md_dfm_unabomb, 15)
```


A lexical dispersion plot highlighting five words is generated
```{r}
#Loading in the quanteda textplots library
library("quanteda.textplots")

#Text is collapsed for the textplot_xray to work
clean_txt_2 <- paste(clean_txt, collapse = " ")
names(clean_txt_2) <- "Unabomber"

#Determining where the following words appear in the text in time
textplot_xray(
  kwic(tokens(clean_txt_2), pattern = "society"),
  kwic(tokens(clean_txt_2), pattern = "kill"),
  kwic(tokens(clean_txt_2), pattern = "leftist"),
  kwic(tokens(clean_txt_2), pattern = "bomb"),
  kwic(tokens(clean_txt_2), pattern = "cleanse"),
  scale = "absolute"
)

```
<br>
<br>

A Wordcloud Print DFM is generared consisting of the top 20 words
```{r}
#This word cloud prints a visual representation of the most common words represented by size
quanteda.textplots::textplot_wordcloud(md_dfm_unabomb, random_order = FALSE, rotation = 0.25) 

#Printing out the top twenty most common words in the text
topfeatures(md_dfm_unabomb, 20)

```
<br>
<br>

## Assignment 5

Modify unambomber so you apply pro template (Done)
  
Improve your cleaning genie so you’re happy rename the genie first name_genie
```{r}
tanaka_genie <- function(text) { 
  
#Loading in stop words from SMART and MIT 
load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/SMART_stops.rda')

load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/MIT_stops.rda')
  
load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/replacements_25.rda')

  #Collapses the string into one text
  clean_corpus <- paste(text, collapse = " ")

  #Standardizes font punctuation not recognized by code to be used in the function
  utf8_normalize <- function(x) {
  stringi::stri_enc_toutf8(as.character(x), is_unknown_8bit = TRUE, validate = TRUE)
}
    
  #Removing unrecognized apostrophes and quotation marks by simpler code
  clean_corpus_apos <- str_replace_all(utf8_normalize(x=clean_corpus),"[\u201c\u201d\u0022\u2033\u02dd\u201f\u201e]", " ")

  #Utilizes lowercase text for all words 
  cl_co_low <- tolower(clean_corpus_apos)
  
  #Removes digits from the text
  cl_co_di <- gsub("[[:digit:]]"," ",cl_co_low)
    
  #Replaces all spaces with a singular space; preparing for splitting and unlisting
  cl_co_sp <- gsub("[[:space:]]"," ", cl_co_di)
    
   #Removing contractions
  cl_co_contractions <- str_replace_all(cl_co_sp, setNames(replacements_25$replacement, nm = replacements_25$word))
 
  #Removing punctuation
  cl_co_punct <- gsub("[[:punct:]]"," ", cl_co_contractions)

  #Splits the words by space
  cl_co_spl = strsplit(cl_co_punct, " ")
    
  #Unlisting the texts in the corpus
  cl_co_unl <- unlist(cl_co_spl)
    
  #Creating a data frame
  df_cleancorpus <- data.frame(Words = cl_co_unl)
    
  #Removing stop words
 df_cleancorpus$Words_No_Stop <- ifelse(
  df_cleancorpus$Words %in% c(MIT_stops$word,SMART_stops$word),
  NA_character_,
  df_cleancorpus$Words
  )
  
 
#### ---- The following options allow for selections of data frames you wish to view
  #Replacing empty spaces with NA (View data frame with two columns: 
  #one with no stopwords removed and another with NAs removed)
  df_cleancorpus$Words_No_Stop[df_cleancorpus$Words_No_Stop == ""] <- NA
 
  #Creating separate data frame with clean words (Contains NAs)
  df_final_NAs <- as.data.frame(dplyr::select(df_cleancorpus, Words_No_Stop))

  #Creating separate data frame with no NAs
  df_final_noNAs <- subset(df_final_NAs, !is.na(Words_No_Stop))
  colnames(df_final_noNAs)[1] <- "Words"
  
  #Returning a new data frame!
    return(df_final_noNAs) 
}
```
  
  
Summarize your corpus with new cleaning data
```{r}
#Importing the unabomber text
unabomb <- paste(readLines('https://raw.githubusercontent.com/Reilly-ConceptsCognitionLab/reillylab_publicdata/main/unabomber_manifesto.txt'))

mycleandat <- tanaka_genie(text=unabomb)
print(mycleandat)

#Loading in the quanteda  library
library(quanteda)

#The data is converted to a corpus for further analysis 
my_simple_corpus <- corpus(mycleandat$Words)

#The corpus is tokenized, removing numbers, punctuation, and separating space
clean_tokenized <- tokens(
  my_simple_corpus,
  remove_numbers = TRUE,
  remove_punct = TRUE,
  remove_separators = TRUE
)

#Showing data for the corpus 
summary(my_simple_corpus)

```
 
  
  Write out your hypothesis about unabomber
```{r}
# Hypothesis
#   The Unabomber texts will be high in anger, intensity, and low in happiness and trust
#   or another way to express this
#   The Unabomber will express and write in a tone to convey paranoia and fear
```
  
  
Run your four variables
```{r}
# load .rda from GitHub raw URL
load(url("https://github.com/Reilly-ConceptsCognitionLab/reillylab_publicdata/blob/main/lookup_Jul25.rda?raw=true"))

lookup_db <- lookup_Jul25
colnames(lookup_db)
str(lookup_db)

# keep join key `word` + columns you want
lookup_small <- lookup_db %>%
  dplyr::select(word, emo_trust, emo_intensity, emo_anxiety, emo_anger)
str(lookup_small)

# join with your text data frame (replace `mycleandat` if your object name differs)
df_prep <- mycleandat %>%
  dplyr::left_join(lookup_small, by = c("Words" = "word"))

print(df_prep)

```


Visualize results
```{r}
#The data is put into a data frame ready for plotting
df_summary <- df_prep %>%
  summarise(
    emo_trust = mean(emo_trust, na.rm = TRUE),
    emo_intensity = mean(emo_intensity, na.rm = TRUE),
    emo_anxiety = mean(emo_anxiety, na.rm = TRUE),
    emo_anger = mean(emo_anger, na.rm = TRUE)
  ) %>%
  pivot_longer(everything(), names_to = "emotion", values_to = "score")

#The plot depicting the variables
ggplot(df_summary, aes(x = reorder(emotion, score), y = score, fill = emotion)) +
  geom_col(width = 0.7) +
  coord_flip() +
  labs(title = "Average Emotion Scores in Clean Text", x = NULL, y = "Mean score") +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none")
```

  
Describe the results in human words
```{r}

# While the unabomber uses intense words, the text is not reflective of him being anxious, angry; however, it does appear that he is not trusting of others.

```


## Assignment 6

1) State a hypothesis about the gaslighting dataset

```{r}

# For those who have never been gaslit, reported definitions of gaslighting are low in intensity

```


2) Develop your processing pipeline and justify steps, etc. 

```{r}

#Loading in lookup database
load(url("https://github.com/Reilly-ConceptsCognitionLab/reillylab_publicdata/blob/main/lookup_Jul25.rda?raw=true"))
lookup_db <- lookup_Jul25
colnames(lookup_db)
str(lookup_db)

#Loading in gaslight corpus
load(url("https://github.com/Reilly-ConceptsCognitionLab/reillylab_publicdata/blob/main/gaslight.rda?raw=true"))

str(gaslight)

#Variables are turned into factors to allow for easier data manipulation
gaslight$Gender <- as.factor(gaslight$Gender)
gaslight$ID <-  as.factor(gaslight$ID)
gaslight$Ever_Gaslit <- as.factor(gaslight$Ever_Gaslit)

#Selecting for gaslight definition
gaslight_definition <- gaslight %>% select(Ever_Gaslit, gd_adult_definition)

#The data is converted to a corpus for further analysis 
my_simple_corpus_gaslight <- corpus(
  gaslight_definition,
  text_field = "gd_adult_definition",
  docvars = gaslight_definition["Ever_Gaslit"]
)

#The corpus is tokenized, removing numbers, punctuation, and separating space
clean_tokenized <- tokens(
  my_simple_corpus_gaslight,
  remove_numbers = TRUE,
  remove_punct = TRUE,
  remove_separators = TRUE
)



#Showing data for the corpus 
summary(my_simple_corpus_gaslight)



```

3) Analyze your data, report relevant statistics and visualization(s)

```{r}
# load .rda from GitHub raw URL
load(url("https://github.com/Reilly-ConceptsCognitionLab/reillylab_publicdata/blob/main/lookup_Jul25.rda?raw=true"))

lookup_db <- lookup_Jul25
colnames(lookup_db)
str(lookup_db)

# keep join key `word` + columns you want
lookup_small <- lookup_db %>%
  dplyr::select(word, emo_intensity)
str(lookup_small)

#Convert to data frame
df_my_simple_corpus_gaslight <- data.frame(
  text_id = quanteda::docnames(my_simple_corpus_gaslight),
  gaslight_definition = as.character(my_simple_corpus_gaslight),
  Ever_Gaslit = quanteda::docvars(my_simple_corpus_gaslight, "Ever_Gaslit"),
  stringsAsFactors = FALSE
)
colnames(df_my_simple_corpus_gaslight)[1] <- "gaslight_definition"

#Makes words unique for the next necessary code
names(df_my_simple_corpus_gaslight) <- make.unique(names(df_my_simple_corpus_gaslight))

#Split words of each definition but retain the text_id
 df_words <- df_my_simple_corpus_gaslight %>%
  mutate(text_id = if ("text_id" %in% names(.)) text_id else rownames(.)) %>%
  select(text_id, Ever_Gaslit, gaslight_definition.1) %>%
  separate_rows(gaslight_definition.1, sep = "\\s+") %>%
  rename(word = gaslight_definition.1) %>%
  mutate(word = tolower(word))


df_prep <- df_words %>%
  dplyr::left_join(lookup_small, by = c("word" = "word"))

print(df_prep)

#Summarize the data for emotional intensity
df_summary_by_text <- df_prep %>%
  group_by(text_id, Ever_Gaslit) %>%
  summarise(
    mean_emo_intensity = mean(emo_intensity, na.rm = TRUE),
    n_matched = sum(!is.na(emo_intensity)),
    .groups = "drop"
  )

#Rearranging the text to order the text_id
df_summary_by_text <- df_summary_by_text[order(as.numeric(sub("text", "", df_summary_by_text$text_id))), ]


#Visualizing results

  #The data is put into a data frame ready for plotting
     df_summary <- df_summary_by_text %>%
        group_by(Ever_Gaslit) %>%
        summarise(
        emo_intensity = mean(mean_emo_intensity, na.rm = TRUE),
        .groups = "drop"
      )

  
  #The plot depicting the variable
  ggplot(df_summary, aes(x = Ever_Gaslit, y = emo_intensity, fill = Ever_Gaslit)) +
  geom_col(width = 0.7) +
  labs(
    title = "Average Emotional Intensity by Gaslighting Experience",
    x = "Ever Gaslit",
    y = "Mean Intensity"
  ) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "none")



```


4) State your conclusions
```{r}

#Based on purely visible observation, those who have never been gaslit give a definition #higher in intensity

```





# Cleaning Genie Repository

## General Cleaning Genie
```{r}

tanaka_genie <- function(z) { 
  
#Loading in stop words from SMART and MIT 
load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/SMART_stops.rda')

load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/MIT_stops.rda')
  
load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/replacements_25.rda')

  #Collapses the string into one text
  clean_corpus <- paste(z, collapse = " ")

  #Standardizes font punctuation not recognized by code to be used in the function
  utf8_normalize <- function(x) {
  stringi::stri_enc_toutf8(as.character(x), is_unknown_8bit = TRUE, validate = TRUE)
}
    
  #Removing unrecognized apostrophes and quotation marks by simpler code
  clean_corpus_apos <- str_replace_all(utf8_normalize(x=clean_corpus),"[\u201c\u201d\u0022\u2033\u02dd\u201f\u201e]", " ")

  #Utilizes lowercase text for all words 
  cl_co_low <- tolower(clean_corpus_apos)
  
  #Removes digits from the text
  cl_co_di <- gsub("[[:digit:]]"," ",cl_co_low)
    
  #Replaces all spaces with a singular space; preparing for splitting and unlisting
  cl_co_sp <- gsub("[[:space:]]"," ", cl_co_di)
    
   #Removing contractions
  cl_co_contractions <- str_replace_all(cl_co_sp, setNames(replacements_25$replacement, nm = replacements_25$word))
 
  #Removing punctuation
  cl_co_punct <- gsub("[[:punct:]]"," ", cl_co_contractions)

  #Splits the words by space
  cl_co_spl = strsplit(cl_co_punct, " ")
    
  #Unlisting the texts in the corpus
  cl_co_unl <- unlist(cl_co_spl)
    
  #Creating a data frame
  df_cleancorpus <- data.frame(Words = cl_co_unl)
    
  #Removing stop words
 df_cleancorpus$Words_No_Stop <- ifelse(
  df_cleancorpus$Words %in% c(MIT_stops$word,SMART_stops$word),
  NA_character_,
  df_cleancorpus$Words
  )
  
 
#### ---- The following options allow for selections of data frames you wish to view
  #Replacing empty spaces with NA (View data frame with two columns: 
  #one with no stopwords removed and another with NAs removed)
  df_cleancorpus$Words_No_Stop[df_cleancorpus$Words_No_Stop == ""] <- NA
 
  #Creating separate data frame with clean words (Contains NAs)
  df_final_NAs <- as.data.frame(dplyr::select(df_cleancorpus, Words_No_Stop))

  #Creating separate data frame with no NAs
  df_final_noNAs <- subset(df_final_NAs, !is.na(Words_No_Stop))
  colnames(df_final_noNAs)[1] <- "Words"
  
  #Returning a new data frame!
    return(df_final_noNAs) 
}
```


## Quanteda Cleaning Genie
```{r}
unabomb_quanteda <- function(z) { 
  
  #Loading in r data stopwords for cleaning
  load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/SMART_stops.rda')
  load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/MIT_stops.rda')
  load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/replacements_25.rda')
  
  # Standardizes font punctuation not recognized by code to be used in the function
  utf8_normalize <- function(x) {
    stringi::stri_enc_toutf8(as.character(x), is_unknown_8bit = FALSE, validate = TRUE)
  }
  
  # Replacing apostrophes and quotes
  unabomb_quanteda_unr.apos <- stringr::str_replace_all(
    utf8_normalize(x = z), 
    "[\u201c\u201d\u0022\u2033\u02dd\u201f\u201e]", " "
  )

  #Applies lowercase to all the text
  unabomb_quanteda_lower <- tolower(unabomb_quanteda_unr.apos)
  
  #Removing digits and spaces
  unabomb_quanteda_digits <- gsub("[[:digit:]]", " ", unabomb_quanteda_lower)
  unabomb_quanteda_space <- gsub("[[:space:]]", " ", unabomb_quanteda_digits)

  #Replacing contractions with the appropriate expansion  
  unabomb_quanteda_contractions <- stringr::str_replace_all(unabomb_quanteda_space, 
    setNames(replacements_25$replacement, nm = replacements_25$word))
 
  #Converting the stopwords columns from each data frame into appropriate form to be able to remove stop words
  sw <- unique(c(MIT_stops$word, SMART_stops$word))
  sw <- sw[nzchar(sw)]
  sw <- gsub("([][{}()+*^$|\\\\?.])", "\\\\\\1", sw)

  unabomb_quanteda_nostops <- gsub(
    paste0("\\b(", paste(sw, collapse = "|"), ")\\b"),
    "",
    unabomb_quanteda_contractions,
    perl = TRUE
  )

  # Removes punctuation except periods by replacing punctuation with spaces
  unabomb_quanteda_punct <- gsub("(?!\\.)[[:punct:]]", " ", unabomb_quanteda_nostops, perl = TRUE)
  #Replaces any and all whitespace into a single space
  unabomb_quanteda_final <- gsub("[[:space:]]+", " ", unabomb_quanteda_punct)
  
  #Cleans up any remaining spaces as a result of removal of punctuation
  unabomb_quanteda_final <- gsub("^ | $", "", unabomb_quanteda_final)

  return(unabomb_quanteda_final) 
}
```


## Gaslight Cleaning Genie
```{r}

gaslight_genie <- function(raw_txt) { 
  
  #Loading in r data stopwords for cleaning
  load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/SMART_stops.rda')
  load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/MIT_stops.rda')
  load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/replacements_25.rda')
  
  # Standardizes font punctuation not recognized by code to be used in the function
  utf8_normalize <- function(x) {
    stringi::stri_enc_toutf8(as.character(x), is_unknown_8bit = FALSE, validate = TRUE)
  }
  
  # Replacing apostrophes and quotes
  gaslight_unr.apos <- stringr::str_replace_all(
    utf8_normalize(x = raw_txt), 
    "[\u201c\u201d\u0022\u2033\u02dd\u201f\u201e]", " "
  )

  #Applies lowercase to all the text
  gaslight_lower <- tolower(gaslight_unr.apos)
  
  #Removing digits and spaces
  gaslight_digits <- gsub("[[:digit:]]", " ", gaslight_lower)
  gaslight_space <- gsub("[[:space:]]", " ", gaslight_digits)

  #Replacing contractions with the appropriate expansion  
  gaslight_contractions <- stringr::str_replace_all(gaslight_space, 
    setNames(replacements_25$replacement, nm = replacements_25$word))
 
  #Converting the stopwords columns from each data frame into appropriate form to be able to remove stop words
  sw <- unique(c(MIT_stops$word, SMART_stops$word))
  sw <- sw[nzchar(sw)]
  sw <- gsub("([][{}()+*^$|\\\\?.])", "\\\\\\1", sw)

  gaslight_nostops <- gsub(
    paste0("\\b(", paste(sw, collapse = "|"), ")\\b"),
    "",
    gaslight_contractions,
    perl = TRUE
  )

  # Removes punctuation except periods by replacing punctuation with spaces
  gaslight_punct <- gsub("[[:punct:]]", " ", gaslight_nostops, perl = TRUE)
  #Replaces any and all whitespace into a single space
  gaslight_final <- gsub("[[:space:]]+", " ", gaslight_punct)
  
  #Cleans up any remaining spaces as a result of removal of punctuation
  gaslight_final <- gsub("^ | $", "", gaslight_final)

  return(gaslight_final) 
}

```

