---
title: "Natural Language Processing Course"
author: "Tanaka Manhede"
date: "`r format(Sys.Date(), '%B %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    css: !expr here::here("/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/styles_templates/jr_19.css")
---

```{r setup, include=F}
knitr::opts_chunk$set(fig.width=8, fig.height=5, fig.align = 'left', fig.path='Figs/', cache.path='Cache/', eval=T, echo=T, tidy=TRUE,  cache=F, message=F, warning=F, stringsAsFactors=F, yaml.eval.expr = TRUE)  

library(xfun)
pkg_attach("tidyverse", "here", "kableExtra", "RCurl", "psych", "knitr", "RColorBrewer", 'dplyr', 'readr', install=T)

jamie.theme <- theme_bw() + theme(axis.line = element_line(colour = "black"), panel.grid.minor = element_blank(), panel.grid.major = element_blank(), panel.border = element_blank(), panel.background = element_blank(), legend.title= element_blank())  #custom theme ggplot2


print.me <- function(x, ...) {
if (nrow(x) > 200){
   len <- 200 
    } else {
       len <- (nrow(x))
}
   x[1:len,] %>%
   kbl(digits=2, align= 'l', booktabs=T) %>%
   kable_styling(fixed_thead = T) %>%
   kable_paper("striped", full_width = T, html_font = "Helvetica", font_size = 12) %>%
   row_spec(0, color = "white", background = "#5b705f", font_size = 12) %>%
   scroll_box(width = "700px", height = "500px") %>%
   asis_output()
}

registerS3method("knit_print", "data.frame", print.me)
#to_R <- read.csv(here("data", "MyRaw.txt")) ---- using 'here' to read in data


# dat <-
# need two columns assigning each word with the Nlett
#
#
#
#install.packages("formatR")
library(formatR)
```
<br>


# RENOVATION UNDERWAY

More content to come...

# Note of the Day:

What are the chances in which lunch and funeral occur in the same 30-word window? The chances are low but never zero...

# Coder's Note

Welcome to my hub! Here, I will be periodically documenting my coding journey. Some code you will see will make you squint your eyes in confusion. Don't fret! Look the other way and recognize that the code works, equivalent to that of duct tape. Over time, I will upgrade from duct tape to b7000. The metaphor may not make sense but all this just to say enjoy the process of my code writing! Throughout the journey, there will be fun tidbits sprinkled throughout the page to distract from the code, don't get side tracked!  


# Code Snippets

Here is a bank of code snippets to help you (more so me) with your coding!

## Code Snippet 1
```{r}

```


# Homework

This is just a simple repository of the homework assignments
<br>

## Homework 1: Worse
<br>
For my first homework I am going to produce is a string called "Mary had a little lamb" in one code block. Then I'm going to split the string to one word per row. Then I'm going to add a variable called Nletters that counts the letters in each word. The other part of your homework is to style your css to your personal needs.

 <br>

So, step one is to produce the string "Mary had a Little Lamb"

```{r}
my_string <- "Mary had a little lamb"

print(my_string)

```

That seemed easy...
<br>

Now, we are going to take the string "Mary had a little lamb" and put it into a data frame that counts the number of letters/characters in each word. The challenge is being able to create a table that I can simply change the string and it will automatically update; so a bit of elbow grease was used, but nevertheless here is the code:

```{r}

#This splits the sentence by word, given that there is a space inserted between each word
words = str_split(my_string, " ")

#This is a data frame that serves to list out the words in the sentence and the number of letters or characters in each word. It has been formated this way so that a different sentence can be inserted and formatted as a data frame
df.lambchops <- data.frame(x = words, y = NA)

#I am renaming the column with more appropriate names. (haha lamb chops)
colnames(df.lambchops)[1] <- "Words"
colnames(df.lambchops)[2] <- "N_letters"

#For the N_letters column, here we are counting the number of characters or letters in each word that has its own row
df.lambchops$N_letters <- nchar(df.lambchops$Words)

print(df.lambchops)

```

All in a good day's work! 
<br>
<br>

## Homework 2: Worser
<br>
Well it looks like we have another assignment, this one took a little more elbow grease than the last time...
Don't mind the mess, but if it works it works (cue chuckle)

First step is loading in the file needed to be cleaned!

1) Read 'sticks_messy.txt' into R

```{r}
#Here, I am loading in the messy_txt to clean
messy_txt <- readLines('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week2_nlp/data/sticks_messy.txt')
  
```
<br>

I combined the next steps into a function called springcleaning!

2) Create a cleaning function with at least three chained procedures
3) Clean the text file using your homemade cleaning function
4) Split the text file into a one-word-per row format

```{r}

springcleaning <- function() { 

#This line removes punctuations and replaces it with no space to push the word token together or removes an extra space
  gonestring.punct <- gsub("[[:punct:]]","",messy_txt) 
#Removes numbers and replaces it with no space to push the word token togetheror removes an extra space
  gonestring.num <- gsub("[[:digit:]]","",gonestring.punct)
#Removes extra abnormal spaces and replaces it with one space to separate word tokens
  gonestring.sp <- gsub("[[:space:]]"," ", gonestring.num) 
#Splits the words by space
  splitstring = strsplit(gonestring.num, " ")
#Unlisting the texts in the file
  splitstring.unlist <- unlist(splitstring)
#This makes a data frame with a word per row
  df_lambchops <- data.frame(x = splitstring.unlist)
#A new data fram is made and excludes cells that are empty
  df_lamb <- df_lambchops %>% filter(x != "")

#Renaming the column for organizational purposes to "Words" instead of "x"
  colnames(df_lamb)[1] <- "Words"
#Returning a new data frame!
  return(df_lamb) 

} 

springcleaning()

```
<br>

Now that the hard part is out of the way, it's all easy from here.

5) Tell me how many words are in the story

```{r}
#I am counting the number of rows since it represents the number of words in the text
nrow(springcleaning())

```
<br>

Oh, another function; well, this one is not that bad.

6) Compute type token ratio

```{r}

ttr <- function() {
#Counting how many words are in the function to find the total word token
  tokens <- nrow(springcleaning())
#Counting the number of unique word tokens in the data frame
  type <- length(unique(springcleaning()$Words))
#Need to make the values of each variable numeric so that I can perform the operation;It will not work on characters
  as.numeric(tokens)
  as.numeric(type)
#Creating a formula to take the number of unique word tokens and divide it by the total number of tokens in the text
  TTR <- type/tokens
  
  return(TTR)
}

ttr()

```

All done! 

Keep an eye out for Homework 3!
<br>
<br>

## Homework 3: Worse-est
<br>
Elbow grease here! 

```{r}

messy_txt <- readLines(
  "/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week2_nlp/data/sticks_messy.txt"
)

```



```{r}


springcleaning2.0 <- function() { 
  
#Loading in stop words from SMART and MIT 
load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/SMART_stops.rda')

load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/MIT_stops.rda')
  
load('/Users/tanakamanhede/Documents/GitHub/project_nlpcourse26/Manhede_RData/Week3_nlp/data/replacements_25.rda')

  
    messy_txt <- gsub("[[:digit:]]","",messy_txt)
    
  #Making all the words in the text lowercase
    gtext.low <- tolower(messy_txt)
    
  #Removing words from the SMART list
    gtext.smart <- gsub(paste0("\\b(", paste(SMART_stops$word, collapse="|"), ")\\b"), "", gtext.low)
  
  #Replacing contractions with their government names; I unlocked a new R code setNames
    gtext.cont <- str_replace_all(gtext.smart, setNames(replacements_25$replacement, replacements_25$word))
    
  #Removing stop words using MIT  (Most Important Text) 
    gtext.MIT <- gsub(paste0("\\b(", paste(MIT_stops$word, collapse="|"), ")\\b"), "", gtext.cont)
 
  #Removing erroneous punctuation from the text
    gtext <- gsub("[[:punct:]]","",gtext.MIT) 
    
  #Removing random spaces from the text
    gtext2 <- gsub("[[:space:]]"," ", gtext) 
              
  #Splits the words by space
    splitstring2.0 = strsplit(gtext2, " ")
    
  #Unlisting the texts in the file
    splitstring.unlist2.0 <- unlist(splitstring2.0)
    
  #This makes a data frame with a word per row (I like lamb chops (literally), so I kept it)
    df_lambchops2.0 <- data.frame(x = splitstring.unlist2.0)
    
  #A new data fram is made and excludes cells that are empty
    df_lamb2.0 <- df_lambchops2.0 %>% filter(x != "")
  
  #Renaming the column for organizational purposes to "Words" instead of "x"
    colnames(df_lamb2.0)[1] <- "Words"
    
  #Returning a new data frame!
    return(df_lamb2.0) 
} 


# *Cracks knuckles* Moment of truth
springcleaning2.0()

```

Let us test this function! It ain't much but it's honest work around here...

```{r}

#For my next feat, I have pulled texts from The Onion to test the cleaning genie2.0!
messy_txt <- c(
  "Facing intense backlash and scrutiny from critics who say the reference book publisher had failed to take all words into consideration, Merriam-Webster was accused of bias Monday after officially selecting ‘dictionary’ as its 2025 word of the year. “Merriam-Webster clearly has a pro-dictionary bias that’s preventing it from considering all words equally,” lexicographer Alison Nielsen wrote in a widely shared social media post that lambasted the Merriam-Webster editorial team, claiming its members had allowed a “personal affinity for looking up words” to cloud their judgment. “I was willing to overlook it last year when their word of the year was ‘definition,’ but I can’t allow myself to turn a blind eye to this. The Merriam-Webster editorial board is stuck in its own media bubble. They need to look around and read a thesaurus once in a while.” At press time, reports confirmed Merriam-Webster appeared to have doubled down by changing the 2025 word of the year to “dictionaries.”", 
  "“I love having this killer coat in the winter, especially when me and my buddies are cruising around and blasting tunes in my old Mustang, which doesn’t have any heat,” said Lockhart, stretching his lean frame over a pool table to sink a bank shot as he spoke to reporters about how he spends much of his time fixing up the muscle car, which has a faded King Cobra decal on the hood. “Bundle Up Our Bad Boys understands that when a guy like me looks good, he feels good. I’ve become more successful in all areas of my life, whether it’s picking up broads, fighting some jock who dissed me, or street racing at night around a deadly bend on the edge of town.”",
  "Stifling their groans as an instructor distributed the wailing infants, students at the Culinary Institute of America were reportedly given a live baby Friday to learn how to care for a bag of flour. “Flour is the most delicate of the pantry staples, and looking after this child for the week will prepare you to deal with the complexities of milled grain,” said Inès Allard, who teaches introduction to baking and pastry at the school, explaining that the students would have to keep the baby from leaking just as they would need to do with an actual sack of processed wheat. “I know it’s not a real bag of flour, but it’s important to take this seriously. And trust me, this is easy mode—babies can be left out in the open, but if you do that with flour, you get ants. If you can’t handle a live infant, then you sure as hell aren’t ready for 10 pounds of ultra-fine pizza flour crafted from the highest-quality varieties of soft wheat.” At press time, reports indicated that many students had already decided it would be too much work to have a flour bag of their own.")
```
All texts are courtesy of The Onion and their talented writers! Please view here: <a href="https://theonion.com/merriam-webster-accused-of-bias-after-dictionary-named-word-of-the-year/" target="_blank">The Onion: Dictionary</a>, <a href="https://theonion.com/community-leather-coat-drive-helps-bad-boys-in-need/" target="_blank">The Onion: Leather Jacket</a>, <a href="https://theonion.com/culinary-students-given-live-baby-to-learn-how-to-care-for-bag-of-flour/">The Onion: Chef Baby</a>


Ta-da! Are you impressed? Probably not, do not answer that.
```{r}

springcleaning2.0()

```

I luv the Onion (sometimes), anyways that is a wrap folks!